Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-06-17 ms/LMA_method.tex
clean raw data

\textbf{RESULTS:}
Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be 9.68\% higher than leaf disc LMA.
The whole-leaf to leaf disc LMA ratio was higher for species with higher leaf tissue density and larger leaf, and their variance was greater for species with lower leaf tissue density and thinner leaves.
Small leaf punch also inflated the ratio.
The extent of ITV only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.09).

@@

In this study, we aimed to investigate the relationship between whole-leaf (including petiole) LMA and leaf disc LMA,
whether the relationship varied with leaf tissue density, leaf area and leaf thickness, and
whether the extent of ITV for each species match between whole-leaf and leaf disc based estimates.
We collected a total of 334 woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
We evaluate the following hypotheses:
(1) whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas (\protect\hyperlink{ref-Niinemets2007}{Niinemets et al., 2007}),
(2) species with higher leaf tissue density, larger and/or thinner leaves would show larger variance and differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles , whereas those effects are likely to be ignored in leaf disc samples, and
(3) the extent of ITV does not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
In addition to leaf morphology, we also investigate the effects of leaf punch size on the relationship between whole-leaf and leaf disc LMA.

@@

We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of species and individuals.
Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and individuals.
In total, our dataset comprised 334 woody species and 1365 individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Appendix S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al. (\protect\hyperlink{ref-Song2017}{2017}); Fei et al. (\protect\hyperlink{ref-Fei2018}{2018}){]}, which covers the wide climate ranges in the distribution of broad-leaved tree species.
The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe below.

@@

To determine what extent LMA values were affected by the different methods, LMA were determined (i) LMA based on a whole leaf including petioles and (ii) LMA based on leaf disc avoiding thick veins (first to second veins).
Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
Two 1.0-cm diameter discs were taken from each leaf in the Yakushima dataset (see Appendix S2 for more details).
Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package \emph{LeafArea} (\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}).
Fresh leaf thickness (LT; mm) was measured using a micrometer in three points at the base, middle and tip of the leaf using a micrometer (Mitutoyo 293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at 0.001 mm.
Thickness of each leaf disc was also measured for the Yunnan dataset but not for the Yakushima dataset, which enables us to estimate whole-leaf and leaf disc leaf tissue density (LD; g cm\textsuperscript{-3}) separately in the Yunnan dataset.
Leaf dry mass (whole leaves including petioles and midribs, and leaf discs) was recorded after drying 80°C for over 48 h to constant weight using an electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a precision at 0.0001 g.
In the subset of Yakushima dataset, leaf lamina and petiole dry mass were also determined separately (80 out of 193 species) to quantify leaf support costs.
Dry mass for leaf discs were recorded 2-3 discs together for each leaf.
Based on those measurements of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
We foucs on LMA in our study and we do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depend on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S3).

@@

There was a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.68\% {[}95\%CI: 8.05, 11.4{]} greater than disc-based estimates in the arithmetic scale.

@@

The extent of intraspecific trait variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig.4).
Although there were no statistical differences in the SMA slope or elevation (SMA slope: 1.116 {[}95\%CI: 0.954, 1.304{]}, SMA intercept: 0.102 {[}95\%CI: -0.174, 0.377{]}), leaf disc LMA had greater CVs than whole-leaf LMA (\emph{t} = -3.19, \emph{d.f.} = 144, \emph{P} \textless{} 0.001).

@@

Leaf disc LMA explained interspecific variations in whole-leaf LMA (\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} = 409, for whole-leaves in \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \emph{R\textsuperscript{2}} = 0.92, \emph{n} = 364 for leaf laminas in \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.68\% differences).
Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix S4).

@@

When the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch (e.g., 1.0-cm in diameter) is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
The effects of leaf tissue density and leaf area are predictable when we used a large leaf punch (Fig. 2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
The ordinary least-squares (OLS) regressions with leaf area as a covariate as following:
(1) log\textsubscript{10}LMA\textsubscript{w} = 0.997 \(\times\) log\textsubscript{10}LMA\textsubscript{d} + 0.0589 \(\times\) log\textsubscript{10}LA,
(2) log\textsubscript{10}LMA\textsubscript{d} = 0.15 + 0.945 \(\times\) log\textsubscript{10}LMA\textsubscript{w} - 0.063 \(\times\) log\textsubscript{10}LA (\emph{R\textsuperscript{2}} = 0.94, \emph{AIC} = -321.7, \emph{n} = 193),
where LMA\textsubscript{w}, LMA\textsubscript{d}, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
Thej OLS regressions without leaf area as a covariate as following:
(3) log\textsubscript{10}LMA\textsubscript{w} = 0.124 + 0.958 \(\times\) log\textsubscript{10}LMA\textsubscript{d} or
(4) log\textsubscript{10}LMA\textsubscript{d} = 0.973 \(\times\) log\textsubscript{10}LMA\textsubscript{w}
(\emph{R\textsuperscript{2}} = 0.93, \emph{AIC} = -284.2, \emph{n} = 193).
Nonetheless, including leaf area only slightly improves the \emph{R\textsuperscript{2}} values for the Yakushima dataset where a large punch was used.
This is because the large discrepancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called ``diminishing returns'' (\protect\hyperlink{ref-Niklas2007}{Niklas et al., 2007}) which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles (\protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}).
This effect is generally strong for mature leaves (\protect\hyperlink{ref-Jiao2022}{Jiao et al., 2022}).
The ``diminishing returns'' can be either described as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
When one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis) or quickly measure leaf disc LMA as a proxy for whole-leaf LMA, we recommend to convert LMA values using one of the models above.

@@

Even though we used the same species, the same individuals and the same trait (LMA) to estimate the extents of intraspecific trait variation (ITV), the explained variance of the relationship between whole-leaf and disc-based estimate was surprisingly small (Fig. 3; \emph{R\textsuperscript{2}} = 0.09).
This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
On average, ITV based on leaf disc LMA was greater than ITV based on whole-leaf LMA as we expected.
Although there are not many studies that quantified trait variation within a single leaf, a previous study that used a giant leaved species \emph{Alocasia macrorrhiza}, suggests that LMA varied within leaves due to reduced water supply and demand from midrib to outer regions (\protect\hyperlink{ref-Li2013a}{Li et al., 2013}).
Because calculating the mean values generally diminishes the effect of within-sample variation, the relationship between disc-based estimates of individual mean LMA and its whole-leaf estimates will be stronger than the relationship between leaf disc CV and whole-leaf CV.
Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to determine sources of trait variation (e.g., site, across species, within species) which often use mixed linear models and variance partitioning (e.g., \protect\hyperlink{ref-Messier2010}{Messier et al., 2010}; \protect\hyperlink{ref-Leps2011}{Lepš et al., 2011}; \protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}).
However, it is likely to change patterns significantly in the type of ITV studies that attempt to quantify the extent of ITV which usually use CV (i.g., \protect\hyperlink{ref-Albert2010a}{Albert et al., 2010}; \protect\hyperlink{ref-Bastias2017a}{Bastias et al., 2017}; \protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estimates but those two estimates are usually not clarified in trait databases (e.g., TRY).
Since we used limited sample numbers (at least 5 samples per species) and most of them were obtained with a small punch, our study design may inflate errors in estimating ITV (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
Future studies should include more samples to improve the comparisons of leaf disc and whole-leaf based ITV.

@@

The authors thank Lian-Bin Tao and Peng-Yun Yan for field work.
This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068).
PM was supported by financial support from CAS-TWAS President's Fellowship for International Doctoral Students.
MK was supported by CAS President's International Fellowship Initiative (2020FYB0003).

>>>>

\textbf{RESULTS:}
Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be 9.69\% higher than leaf disc LMA.
The whole-leaf to leaf disc LMA ratio was higher for species with higher leaf tissue density and larger leaf, and their variance was greater for species with lower leaf tissue density and thinner leaves.
Small leaf punch also inflated the ratio.
The extent of ITV only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.08).

@@

In this study, we aimed to investigate the relationship between whole-leaf (including petiole) LMA and leaf disc LMA,
whether the relationship varied with leaf tissue density, leaf area and leaf thickness, and
whether the extent of ITV for each species match between whole-leaf and leaf disc based estimates.
We collected leaves from 1459 individuals of 334 woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
We evaluate the following hypotheses:
(1) whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas (\protect\hyperlink{ref-Niinemets2007}{Niinemets et al., 2007}),
(2) species with higher leaf tissue density, larger and/or thinner leaves would show larger variance and differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles , whereas those effects are likely to be ignored in leaf disc samples, and
(3) the extent of ITV does not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
In addition to leaf morphology, we also investigate the effects of leaf punch size on the relationship between whole-leaf and leaf disc LMA.

@@

We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of 141 species and 852 individuals.
Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and 607 individuals.
In total, our dataset comprised 334 woody species and 1459 individuals that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Appendix S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al. (\protect\hyperlink{ref-Song2017}{2017}); Fei et al. (\protect\hyperlink{ref-Fei2018}{2018}){]}, which covers the wide climate ranges in the distribution of broad-leaved tree species.
The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe below.

@@

To determine what extent LMA values were affected by the different methods, LMA were determined (i) LMA based on a whole leaf including petioles and (ii) LMA based on leaf disc avoiding thick veins (first to second veins).
Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
Two 1.0-cm diameter discs were taken from each leaf in the Yakushima dataset (see Appendix S2 for more details).
Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package \emph{LeafArea} (\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}).
Fresh leaf thickness (LT; mm) was measured using a micrometer in three points at the base, middle and tip of the leaf (Mitutoyo 293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at 0.001 mm.
Thickness of each leaf disc was also measured for the Yunnan dataset but not for the Yakushima dataset, which enables us to estimate whole-leaf and leaf disc leaf tissue density (LD; g cm\textsuperscript{-3}) separately in the Yunnan dataset.
Leaf dry mass (whole leaves including petioles and midribs, and leaf discs) was recorded after drying 80°C for over 48 h to constant weight using an electronic scale (Mettler-Toledo MS204TS, Columbus, Ohio, U.S.A.) with a precision at 0.0001 g.
In the subset of Yakushima dataset, leaf lamina and petiole dry mass were also determined separately (80 out of 193 species) to quantify leaf support costs.
Dry mass for leaf discs were recorded 2-3 discs together for each leaf.
Based on those measurements of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
We foucs on LMA in our study and we do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depend on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S3).

@@

There was a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.69\% {[}95\%CI: 8.06, 11.3{]} greater than disc-based estimates in the arithmetic scale.

@@

The extent of intraspecific trait variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig.4).
Although there were no statistical differences in the SMA slope or elevation (SMA slope: 1.112 {[}95\%CI: 0.951, 1.302{]}, SMA intercept: 0.096 {[}95\%CI: -0.18, 0.372{]}), leaf disc LMA had greater CVs than whole-leaf LMA (\emph{t} = -3.2, \emph{d.f.} = 143, \emph{P} \textless{} 0.001).

@@

Leaf disc LMA explained interspecific variations in whole-leaf LMA (\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} = 409, for whole-leaves in \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \emph{R\textsuperscript{2}} = 0.92, \emph{n} = 364 for leaf laminas in \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.69\% differences).
Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix S4).

@@

When the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch (e.g., 1.0-cm in diameter) is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
The effects of leaf tissue density and leaf area are predictable when we used a large leaf punch (Fig. 2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
The ordinary least-squares (OLS) regressions with leaf area as a covariate as following:
(1) log\textsubscript{10}LMA\textsubscript{w} = 0.997 \(\times\) log\textsubscript{10}LMA\textsubscript{d} + 0.0589 \(\times\) log\textsubscript{10}LA,
(2) log\textsubscript{10}LMA\textsubscript{d} = 0.15 + 0.945 \(\times\) log\textsubscript{10}LMA\textsubscript{w} - 0.063 \(\times\) log\textsubscript{10}LA (\emph{R\textsuperscript{2}} = 0.94, \emph{AIC} = -321.7, \emph{n} = 193),
where LMA\textsubscript{w}, LMA\textsubscript{d}, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
The OLS regressions without leaf area as a covariate as following:
(3) log\textsubscript{10}LMA\textsubscript{w} = 0.124 + 0.958 \(\times\) log\textsubscript{10}LMA\textsubscript{d} or
(4) log\textsubscript{10}LMA\textsubscript{d} = 0.973 \(\times\) log\textsubscript{10}LMA\textsubscript{w}
(\emph{R\textsuperscript{2}} = 0.93, \emph{AIC} = -284.2, \emph{n} = 193).
{[}Note that OLS regressions minimize errors of either whole-leaf LMA or leaf disc LMA, and thus those four models are not identical, whereas SMA regressions are not appropriate for predictions (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}){]}
Nonetheless, including leaf area only slightly improves the \emph{R\textsuperscript{2}} values for the Yakushima dataset where a large punch was used.
This is because the large discrepancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called ``diminishing returns'' (\protect\hyperlink{ref-Niklas2007}{Niklas et al., 2007}) which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles (\protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}).
This effect is generally strong for mature leaves (\protect\hyperlink{ref-Jiao2022}{Jiao et al., 2022}).
The ``diminishing returns'' can be either described as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
When one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis) or quickly measure leaf disc LMA as a proxy for whole-leaf LMA, we recommend to convert LMA values using one of the models above.

@@

Even though we used the same species, the same individuals and the same trait (LMA) to estimate the extents of intraspecific trait variation (ITV), the explained variance of the relationship between whole-leaf and disc-based estimate was surprisingly small (Fig. 3; \emph{R\textsuperscript{2}} = 0.08).
This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
On average, ITV based on leaf disc LMA was greater than ITV based on whole-leaf LMA as we expected.
Although there are not many studies that quantified trait variation within a single leaf, a previous study that used a giant leaved species \emph{Alocasia macrorrhiza}, suggests that LMA varied within leaves due to reduced water supply and demand from midrib to outer regions (\protect\hyperlink{ref-Li2013a}{Li et al., 2013}).
Because calculating the mean values generally diminishes the effect of within-sample variation, the relationship between disc-based estimates of individual mean LMA and its whole-leaf estimates will be stronger than the relationship between leaf disc CV and whole-leaf CV.
Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to determine sources of trait variation (e.g., site, across species, within species) which often use mixed linear models and variance partitioning (e.g., \protect\hyperlink{ref-Messier2010}{Messier et al., 2010}; \protect\hyperlink{ref-Leps2011}{Lepš et al., 2011}; \protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}).
However, it is likely to change patterns significantly in the type of ITV studies that attempt to quantify the extent of ITV which usually use CV (i.g., \protect\hyperlink{ref-Albert2010a}{Albert et al., 2010}; \protect\hyperlink{ref-Bastias2017a}{Bastias et al., 2017}; \protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estimates but those two estimates are usually not clarified in trait databases (e.g., TRY).
Since we used limited sample numbers (at least 5 samples per species) and most of them were obtained with a small punch, our study design may inflate errors in estimating ITV (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
Future studies should include more samples to improve the comparisons of leaf disc and whole-leaf based ITV.

@@

We thank the editors and two anonymous reviewers, whose comments greatly improved the manuscript.
We also thank Lian-Bin Tao and Peng-Yun Yan for field work.
This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068).
PM was supported by financial support from CAS-TWAS President's Fellowship for International Doctoral Students.
MK was supported by CAS President's International Fellowship Initiative (2020FYB0003).
